\worksheet{Super-Sized Super Bowl}

\textbf{Weight and NFL Defensive Tackles}

Each roll simulates pulling a random player who has played defensive line or defensive tackle in the NFL.
\begin{enumerate}
	\item Roll two dice (or one die twice)
	\item If you roll a 12 (two 6's), then your player weighs at least 325 pounds.
	\item Else, your player weighs less than the Fridge.
\end{enumerate}

Try it several times. Did you get anyone heavier than Perry? If so, how many?\vfill

\textbf{Two Point Conversions}

In the NFL, after a touch-down is scored, the team has the choice of kicking the ball through the goal posts for one extra point or physically getting the ball to an offensive player in the end zone for two extra points. Which choice the coach makes depends on a lot of different factors including the skill of their players, but the main decision factor is often the difference in points that the team has compared to their opponent.

\begin{enumerate}
	\item \textbf{Game Situation 1: Team A trailing by 8 points (16-24) with 5 minutes left in the 4th quarter.}
After scoring a touchdown, what should Team A's coach call?

Probabilities: 
\begin{itemize}
	\item Probability of successfully converting a two-point conversion: 45%
	\item Probability of successfully converting an extra point kick: 95%
	\item Probability of stopping the opponent and getting another possession: 30% 
\end{itemize}
Calculate the expected points gained by attempting a two-point conversion versus an extra point kick and the probability of winning the game based on these numbers.  

What are some additional complications that you would want to build into the decision-making analytics if you had more time?
\vfill

\item Game Situation 2: Team B leading by 6 points (21-15) with 2 minutes left in the 4th quarter.
After scoring a touchdown, what should Team B's coach call?

Probabilities:
\begin{itemize}
	\item Probability of successfully converting a two-point conversion: 50%
	\item Probability of successfully converting an extra point kick: 97%
	\item Probability of stopping the opponent and getting another possession: 40%
\end{itemize}

Determine whether attempting a two-point conversion in this situation is the right call for Team B. 

What are some additional complications that you would want to build into the decision-making analytics if you had more time?\vfill

\end{enumerate}
