\worksheet{Racking Up The Wins}
\begin{enumerate}
	\item The UConn women's basketball team won 111 straight games. How many can you win?
\begin{enumerate}
	\item Calculate the probability that if you roll three dice, you don't get three ones. \vfill
	\item Roll three dice (or one dice three times) to see if you win or lose a game.  If you don't want to actually roll the dice, you can open up a browser and type ``roll dice'' into Google, then click the square two more times to get three six-sided dice to roll. 
	\item If you get three ones, you lose the game; else you win.
	\item Repeat this until you lose a game or win 111 games. Tally your winning streak with the chart below.
	
	\begin{center}
		\begin{tikzpicture}[scale=.8]
		\foreach \x in {1,...,11}{
       \node [inner sep=10pt, draw] at  (\x,0)  {};
			}
		 \foreach \x in {1,...,20}{
		\foreach \y in {1,...,5}{
       \node [inner sep=10pt, draw] at  (\x,\y)  {};
       }
			}
	\end{tikzpicture}
	\end{center}
	\vfill
\end{enumerate}
\item What is a factorial and what is the formula for \(10!\)?\vfill
\clearpage
\item What is a permutation? What is the formula for \(P(8,3)\)? If there are 8 Varsity Cross-Country runners, how many ways can they take first, second, and third place in one race? \vfill
\item What is a combination? What is the formula for \(C(9,4)\)? How many ways can Wartburg Men's Soccer team tie 4 of their first 9 games ? \vfill
\item What is the formula for the probability of \(r\) successes out of \(n\) attempts where the probability of each success is \(p\)? Georgia Nissen has an overall tennis singles record of 4-2, use that record to calculate the probability that she wins 3 of her next 4 games? \vfill
\end{enumerate}